Random Tree Search Algorithm for Nash Equilibrium in Capacitated Selfish Replication Games

### 2016-03-10 doc/paper.tex
bugfix

\begin{document}
\title{Random Tree Search Algorithm for Nash Equilibrium in Capacitated Selfish
Replication Games}
\author{\authorblockN{Seyed Nematollah Ahmadian\textdagger, Seyed Rasoul Etesami\textdaggerdbl, H. Vincent Poor\textdaggerdbl}
  \authorblockA{}
\thanks{\textdagger Seyed Nematollah Ahmadian is with
Coordinated Science Laboratory,
Department of Electrical and Computer Engineering,
University of Illinois at Urbana-Champaign, Urbana, IL, 61801;
E-mail: {ahmadya2}@illinois.edu}
\thanks{
\textdaggerdbl Seyed Rasoul Etesami and H. Vincent Poor are with
Department of Electrical Engineering,
Princeton University, NJ, 08644;
E-mail: etesami,poor@Princeton.EDU}
}
\maketitle
\input{abstract.tex}
\input{introduction.tex}
\input{problem.tex}
\input{motivation.tex}
\input{algorithm.tex}
\input{conclusion.tex}
\bibliographystyle{IEEEtran}
\bibliography{thesisrefs}
\end{document}

>>>>

\begin{document}
\title{Random Tree Search Algorithm for Nash Equilibrium in Capacitated Selfish
Replication Games}
\author{\authorblockN{Seyed Nematollah Ahmadyan\textdagger, Seyed Rasoul Etesami\textdaggerdbl, H. Vincent Poor\textdaggerdbl}
  \authorblockA{}
\thanks{\textdagger Seyed Nematollah Ahmadyan is with
Coordinated Science Laboratory,
Department of Electrical and Computer Engineering,
University of Illinois at Urbana-Champaign, Urbana, IL, 61801;
E-mail: {ahmadya2}@illinois.edu}
\thanks{
\textdaggerdbl Seyed Rasoul Etesami and H. Vincent Poor are with
Department of Electrical Engineering,
Princeton University, NJ, 08644;
E-mail: etesami,poor@Princeton.EDU}
}
\maketitle
\input{abstract.tex}
\input{introduction.tex}
\input{problem.tex}
\input{motivation.tex}
\input{algorithm.tex}
\input{conclusion.tex}
\bibliographystyle{IEEEtran}
\bibliography{thesisrefs}
\end{document}
